Minimum Regret Search for Single- and Multi-Task Optimization

### 2016-05-18 2016_ICML/cmrs.tex
Format corrections and some minor changes

\documentclass{article} % For LaTeX2e

@@

\usepackage{umoline}
%\newcommand{\todo}[2]{\Underline{#1}\textbf{ [\scriptsize TODO: #2] }}
\newcommand{\todo}[2]{#1}

@@

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2015
% package.
\icmlauthor{Jan Hendrik Metzen}{janmetzen@mailbox.org}
\icmladdress{Universit{\"a}t Bremen, 28359 Bremen, Germany \&
             Robert Bosch GmbH, 70442 Stuttgart, Germany}
%\icmlauthor{Your CoAuthor's Name}{email@coauthordomain.edu}
%\icmladdress{Their Fantastic Institute,
%            27182 Exp St., Toronto, ON M6H 2T1 CANADA}

@@

Bayesian optimization \citep[BO,][]{shahriari_taking_2016} denotes a sequential,
model-based, global approach for optimizing black-box functions that are
non-convex, do not necessarily provide derivatives, are expensive to evaluate (either
computationally, economically, or morally), and are potentially noisy. Under
these conditions, there is typically no guarantee for finding the true optimum of the
function with a finite number of function evaluations. Instead, one often aims
at finding a solution which has small \emph{immediate regret} with regard to the true optimum, where 
``immediate regret'' denotes the difference of function value of the selected solution to 
true the optimal function value. BO
aims at finding such a solution of minimum immediate regret while  minimizing at the same
time the number of evaluations of the expensive target function. For this, BO
maintains a probabilistic surrogate model of the objective function, and a
myopic utility or acquisition function, which defines the ``usefulness'' of
performing an additional function evaluation at a certain input for learning about the optimum.

@@

In this section, we provide a brief overview of
\textbf{Bayesian Optimization} (BO). We refer to \citet{shahriari_taking_2016} for a recent more
extensive review of BO. BO can be applied to black-back optimization
problems, which can be framed as optimizing an objective function $f:
\mathcal{X} \to \mathbb{R}$ on some bounded set $\mathcal X \subset
\mathbb{R}^D$. In contrast to most  other black-box optimization methods, BO is
a global method which makes use of all historic evaluations of $f(\mathbf{x})$
rather than using only a subset of the history for approximating a local
gradient or Hessian. For this, BO maintains a \emph{probabilistic model} for
$f(\mathbf{x})$, typically a Gaussian process \citep[GP,][]{rasmussen_gaussian_2006}, and uses this model for deciding
at which $\mathbf{x}_{n+1}$ the function $f$ will be evaluated next.

@@

\subsection{Formulation}
Let $X \subset \mathcal{R}^D$ be some bounded domain and $f: \mathcal{X} \mapsto
\mathbb{R}$ be a function. We are interested in finding the maximum
$\mathbf{x}^\star$ of $f$ on $\mathcal{X}$. Let there be a probability measure
$p(f)$ over the space of functions $f: \mathcal{X} \mapsto \mathbb{R}$, such as
a GP. Based on this $p(f)$, we would ultimately like to
select an $\mathbf{\tilde x}$ which has minimum immediate regret
$R_f(\mathbf{\tilde x})$. We define the expected immediate regret ER of
selecting parameter $\mathbf{x}$ under $p(f)$ as follows:
$$\text{ER}(p)(\mathbf{x}) = \mathbb{E}_{p(f)}[R_f(\mathbf{x})]
= \mathbb{E}_{p(f)}[\max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{
x})]$$
The minimizer $\mathbf{\tilde x}$ of the expected immediate regret under fixed $p(f)$ can be determined efficiently in the case of a GP since it is identical to the maximizer of the GP's mean $\mu_N(\mathbf{x})$. However, in general, $p(f)$ depends on data and it is desirable to select the data such that $\text{ER}$ is also minimized with regard to the resulting $p(f)$.

>>>>

\documentclass[10pt,letterpaper]{article} % For LaTeX2e

@@

\usepackage{times}

@@

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2015
% package.
\icmlauthor{Jan Hendrik Metzen}{janmetzen@mailbox.org}
\icmladdress{Universit{\"a}t Bremen, 28359 Bremen, Germany \\
             Robert Bosch GmbH, 70442 Stuttgart, Germany}
%\icmlauthor{Your CoAuthor's Name}{email@coauthordomain.edu}
%\icmladdress{Their Fantastic Institute,
%            27182 Exp St., Toronto, ON M6H 2T1 CANADA}

@@

Bayesian optimization \citep[BO,][]{shahriari_taking_2016} denotes a sequential,
model-based, global approach for optimizing black-box functions that are
non-convex, do not necessarily provide derivatives, are expensive to evaluate (either
computationally, economically, or morally), and are potentially noisy. Under
these conditions, there is typically no guarantee for finding the true optimum of the
function with a finite number of function evaluations. Instead, one often aims
at finding a solution which has small \emph{immediate regret} with regard to the true optimum, where 
``immediate regret'' denotes the difference of the true optimal function value 
and the function value of the selected solution. BO
aims at finding such a solution of minimum immediate regret while  minimizing at the same
time the number of evaluations of the expensive target function. For this, BO
maintains a probabilistic surrogate model of the objective function, and a
myopic utility or acquisition function, which defines the ``usefulness'' of
performing an additional function evaluation at a certain input for learning about the optimum.

@@

In this section, we provide a brief overview of
\textbf{Bayesian Optimization} (BO). We refer to \citet{shahriari_taking_2016} for a recent more
extensive review of BO. BO can be applied to black-box optimization
problems, which can be framed as optimizing an objective function $f:
\mathcal{X} \to \mathbb{R}$ on some bounded set $\mathcal X \subset
\mathbb{R}^D$. In contrast to most  other black-box optimization methods, BO is
a global method which makes use of all previous evaluations of $f(\mathbf{x})$
rather than using only a subset of the history for approximating a local
gradient or Hessian. For this, BO maintains a \emph{probabilistic model} for
$f(\mathbf{x})$, typically a Gaussian process \citep[GP,][]{rasmussen_gaussian_2006}, and uses this model for deciding
at which $\mathbf{x}_{n+1}$ the function $f$ will be evaluated next.

@@

\subsection{Formulation}
Let $\mathcal{X} \subset \mathcal{R}^D$ be some bounded domain and $f: \mathcal{X} \mapsto
\mathbb{R}$ be a function. We are interested in finding the maximum
$\mathbf{x}^\star$ of $f$ on $\mathcal{X}$. Let there be a probability measure
$p(f)$ over the space of functions $f: \mathcal{X} \mapsto \mathbb{R}$, such as
a GP. Based on this $p(f)$, we would ultimately like to
select an $\mathbf{\tilde x}$ which has minimum immediate regret
$R_f(\mathbf{\tilde x})$. We define the expected immediate regret ER of
selecting parameter $\mathbf{x}$ under $p(f)$ as follows:
$$\text{ER}(p)(\mathbf{x}) = \mathbb{E}_{p(f)}[R_f(\mathbf{x})]
= \mathbb{E}_{p(f)}[\max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{
x})]$$
The minimizer $\mathbf{\tilde x}$ of the expected immediate regret under fixed $p(f)$ can be determined efficiently in the case of a GP since it is identical to the maximizer of the GP's mean $\mu_N(\mathbf{x})$. However, in general, $p(f)$ depends on data and it is desirable to select the data such that $\text{ER}$ is also minimized with regard to the resulting $p(f)$.
